---
title: "DRAFT::: Grade profiles"
---

```{r global-options, include=FALSE}
# Set echo=false for all chunks
knitr::opts_chunk$set(echo=FALSE)
```

*Please note that this is a draft piece of analysis which has not yet undergone full quality assurance. Do not use this research for any purpose until this message is removed.*

Below are links to grade-specific profiles. These contain the outputs present on the summary statistics page, filtered by grade. Only grades with 20 or more respondents are included.

## Department sample sizes

``` {r}

library(magrittr)

if(!exists("data")) stop("Dataframe called data not available. This should be in the function enviroment of render_main_site. Check that this is available in this enviroment.")

grade_freqs <- data.frame(table(data$grade))
grade_freqs <- grade_freqs[grade_freqs[2] >= 20, ]
grade_freqs[1] <- as.character(grade_freqs[[1]])
colnames(grade_freqs) <- c("Department", "Sample size")

carsurvey2::setup_table_toggle()
carsurvey2::insert_table_toggle("dep-freqs")

```

<div id="dep-freqs-chart">
``` {r}

freqs_plot <- grade_freqs
freqs_plot[1] <- stringr::str_wrap(freqs_plot[[1]], width = 40)
freqs_plot[1] <- gsub("\\n", "<br>", freqs_plot[[1]])
freqs_plot <- freqs_plot[rev(order(freqs_plot[1])), ]
freqs_plot[1] <- factor(freqs_plot[[1]], levels = freqs_plot[[1]])
carsurvey2::plot_freqs(freqs_plot, "", "Sample size", n = sum(freqs_plot$`Sample size`), font_size = 14, orientation = "h", height = 400)

```
</div>

<div id="dep-freqs-table">
``` {r}

kableExtra::kable_styling(knitr::kable(freqs_plot, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", sum(freqs_plot$`Sample size`)))

```
</div>


``` {r}

grades <- data.frame(table(data$grade))
grades_list <- grades[grades[2] >= 20, ]

alphabetical <- as.character(grades_list$Var1[order(grades_list[[1]])])
urls <- gsub(" \\(excl. agencies\\)", "", alphabetical)
urls <- gsub(" ", "-", urls)
urls <- gsub(",", "", urls)
links <- paste0('<li><a href="', urls, '.html">', alphabetical, "</a></li>")
html <- paste(links, collapse="\n\n")
html <- paste0("<ol>", html, "</ol>")
knitr::raw_html(html)

```

