---
title: "Coding frequency and tools"
---

## Coding frequency

We asked our respondents, "In my current role, I write code to complete my work objectives _____". The frequencies for each answer are presented below. 

```{r echo=FALSE}
carsurvey2::setup_table_toggle()
```

```{r echo=FALSE}
carsurvey2::insert_table_toggle("coding-freq")
```

<div id="coding-freq-chart" style="width: 100vw">
```{r echo=FALSE}

carsurvey2::plot_freqs(freq_table, "Coding frequency", "Count", font_size = 14)

```
</div>

<div id="coding-freq-table">
```{r echo = FALSE}

knitr::kable(freq_table)

```
</div>


## Programming languages - access and knowledge

For each of the most popular programming languages from last year's CARS data, we asked respondents to answer "yes", "no" or "I don't know" for the following statements: 

* I know how to program with this tool to a level suitable for my work
* This tool is available to use for my work

### Knowledge of programming tools

```{r echo=FALSE}
carsurvey2::insert_table_toggle("tools-knowledge")
```

<div id="tools-knowledge-chart">
```{r echo=FALSE}

carsurvey2::plot_stacked(knowledge, xlab = "Count", ylab = "Programming tool", font_size = 14)

```
</div>

<div id="tools-knowledge-table">
```{r echo = FALSE}

knitr::kable(knowledge, row.names = FALSE)

```
</div>


### Access to programming tools

```{r echo=FALSE}
carsurvey2::insert_table_toggle("tools-access")
```

<div id="tools-access-chart">
```{r echo=FALSE}

carsurvey2::plot_stacked(access, xlab = "Count", ylab = "Programming tool", font_size = 14)

```
</div>

<div id="tools-access-table">
```{r echo = FALSE}

knitr::kable(access, row.names = FALSE)

```
</div>


### Access and knowledge gaps

We used the above data to calculate the number of respondents who have access but no knowledge, access and knowledge, and knowledge but no access for each programming language. The results can be seen below.


```{r echo=FALSE}
carsurvey2::insert_table_toggle("tools-status")
```

<div id="tools-status-chart">
```{r echo=FALSE}

carsurvey2::plot_stacked(code_tool_status, colour_scale = "scale",xlab = "Count", ylab = "Programming tool", font_size = 14)


```
</div>

<div id="tools-status-table">
```{r echo = FALSE}

knitr::kable(code_tool_status, row.names = FALSE)

```
</div>

