---
title: "RAP knowledge and opinions"
---

```{r echo=FALSE}
carsurvey2::setup_table_toggle()
```


## Knowledge of RAP and RAP champions

We asked our respondents whether they had heard of RAP and what their knowlegde is of their own department RAP champion. The combined responses are presented below.

```{r echo=FALSE}
carsurvey2::insert_table_toggle("rap-knowledge")
```

<div id="rap-knowledge-chart">
```{r echo=FALSE}

carsurvey2::plot_freqs(rap_knowledge_chart, "Knowledge of RAP champions", "Count", font_size = 14, orientation = "h")

```
</div>

<div id="rap-knowledge-table">
```{r echo = FALSE}

knitr::kable(rap_knowledge, row.names = FALSE)

```
</div>


## Opinions on RAP

We aked our respondents who had heard of RAP the extent to which they agree with the following statements:

* "I understand what the key components of the RAP methodology are"
* "I feel confident implementing RAP in my work"
* "I think it is important to implement RAP in my work"
* "I feel supported to implement RAP in my work"
* "I know where to find resources to help me implement RAP"
* "I and/or my team are currently implementing RAP"

The results can be seen below. The figure and table show the percentage of respondents who picked each response option. Percentages are out of a sample of respondents who said they had heard of RAP.


```{r echo=FALSE}
carsurvey2::insert_table_toggle("rap-opinions")
```

<div id="rap-opinions-chart">
```{r echo=FALSE}

carsurvey2::plot_likert(rap_opinions_chart, 3, "Question", "Response", font_size = 14)

```
</div>

<div id="rap-opinions-table">
```{r echo = FALSE}

knitr::kable(rap_opinions, row.names = FALSE)

```
</div>

