---
title: "RAP scores"
---

```{r echo=FALSE}
carsurvey2::setup_table_toggle()
```


## RAP components

The frequencies for each RAP component below are derived from a series of questions on coding practices (see the coding practices page). These were used to calculate scores for each component (0/1) where respondents answered "regularly" or "all the time" to the relevant questions. The list of RAP components used here is based on the [RAP minimum viable product](https://github.com/best-practice-and-impact/rap_mvp_maturity_guidance/blob/master/Reproducible-Analytical-Pipelines-MVP.md) guidance agreed by the RAP champions network.

```{r echo=FALSE}
carsurvey2::insert_table_toggle("rap-comps")
```

<div id="rap-comps-chart">
```{r echo=FALSE}

carsurvey2::plot_grouped(components, "RAP component", "Count", orientation = "h", font_size = 14)


```
</div>

<div id="rap-comps-table">
```{r echo = FALSE}

kableExtra::kable_styling(knitr::kable(components, row.names = FALSE))

```
</div>

### RAP scores

Below are the distributions of total basic and advanced RAP scores. These are the sum of the scores for each RAP component.

#### Basic RAP scores:

```{r echo=FALSE}
carsurvey2::insert_table_toggle("basic_score")
```

<div id="basic_score-chart">
```{r echo=FALSE}

bar_colour <- carsurvey2::get_2colour_scale(2)[2][[1]]
bar_colour <- rgb(bar_colour[1],bar_colour[2],bar_colour[3], maxColorValue = 255)
carsurvey2::plot_freqs(basic_freqs, "Basic RAP score", "Count", bar_colour = bar_colour, font_size = 14)

```
</div>

<div id="basic_score-table">
```{r echo = FALSE}

kableExtra::kable_styling(knitr::kable(basic_freqs, row.names = FALSE))

```

#### Advanced RAP scores:

```{r echo=FALSE}
carsurvey2::insert_table_toggle("advanced_score")
```

<div id="advanced_score-chart">
```{r echo=FALSE}

carsurvey2::plot_freqs(advanced_freqs, "Advanced RAP score", "Count", font_size = 14)

```
</div>

<div id="advanced_score-table">
```{r echo = FALSE}

kableExtra::kable_styling(knitr::kable(advanced_freqs, row.names = FALSE))

```